Different forms of uncertainty differently affect the evolution of social learning

### 2022-10-11 ms.tex
added timeseries figure

>>>>

\begin{figure}
    \caption{Example time series of geometric moving average (GMA) with window of 3
      of payoffs from three select simulations (see main text), broken out by 
    social learners, asocial learners, and whole population, compared with the
    expected homogenous social and asocial population payoffs. 
    Social learner prevalence is also plotted. Vertical lines indicate
  environmental change.}
    \label{fig:payoffTimeseries}
  \centering

\vspace{1em}
\hspace{-2em}
  \begin{subfigure}[]{0.75\textwidth}
      \centering
      \caption{$\pilow=0.1$, $B=2$, $L=4$, $u=0.2$}
      \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.2-lowpayoff=0.1-nbehaviors=2-L=4.pdf}
    \end{subfigure} \\

\hspace{-2em}
    \begin{subfigure}[]{0.75\textwidth}
      \centering
      \caption{$\pilow=0.1$, $B=2$, $L=8$, $u=0.2$}
      \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.2-lowpayoff=0.1-nbehaviors=2-L=8.pdf}
    \end{subfigure} \\

\hspace{-2em}
    \begin{subfigure}[]{0.75\textwidth}
      \centering
    \caption{$\pilow=0.1$, $B=4$, $L=1$, $u=0.5$}
      \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.5-lowpayoff=0.1-nbehaviors=4-L=1.pdf}
    \end{subfigure}
    % \\
    % \begin{subfigure}[]{0.6\textwidth}
    %   \centering
    %   \caption{$\pilow=0.1$, $B=10$, $L=20$, $u=0.5$}
    %   \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.5-lowpayoff=0.1-nbehaviors=10-L=20.pdf}
    % \end{subfigure}

\end{figure}
